Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-15 paper/paper.qmd
modify paper

## Treatment Variables
We treated the `treatment_status` variable by creating dummy variables for each type of financial support, resulting in four different treatment levels:
- **Control ()**: 
- **Other()**
# TODO: ADD variable name and explanation for four different treatment dummies

...

@@

- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business. An individual does not have business if they do not have project or have no income source.
- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. It is defined by the sum of inventory stocks, finished goods, liquid cash reserves, value of new business premises, recently purchased land, furniture, machinery and equipment, vehicles, and the cost of maintenance for these assets. 
- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention.
- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.
- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.
- **Labour Income (`labour_inc`)**: It is calculated by summing the monthly profit, wage income, and other labour income source.
- **Total Income (`total_inc`)**: It is calculated by summing the monthly profit, wages, rental income from assets, other income streams not categorized as labor income, government support values, and received transfers.

@@

# Conclusion:

@@

>>>>

## Treatment Variables
We treated the `treatment_status` variable by creating dummy variables for each type of financial support, resulting in four different treatment levels:

- **Loans (`micro_credit`)**: Dummy variable indicating whether the participant received loans. A loan is a sum of money that is borrowed, often from a bank or financial institution, that is expected to be paid back with interest.

- **Cash Grants (`cash_grant`)**: Dummy variable indicating whether the participant received cash grant. Cash grants are funds that are given to individuals, businesses, or organizations for a specific purpose and do not need to be repaid.

- **In-Kind Grants (`in_kind_grant`)**: Dummy variable indicating whether the participant received in-kind grant. In-kind grants include goods or services provided to the entrepreneur that have a direct utility in the business but are not monetary in form. Like cash grants, in-kind grants do not need to be repaid.

- **Control (`control`)**: Dummy variable indicating whether the participant received any financial intervention.

@@

- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business. An individual does not have business if they do not have project or have no income source.

- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. It is defined by the sum of inventory stocks, finished goods, liquid cash reserves, value of new business premises, recently purchased land, furniture, machinery and equipment, vehicles, and the cost of maintenance for these assets.

- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention.

- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.

- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.

- **Labour Income (`labour_inc`)**: It is calculated by summing the monthly profit, wage income, and other labour income source.

- **Total Income (`total_inc`)**: It is calculated by summing the monthly profit, wages, rental income from assets, other income streams not categorized as labor income, government support values, and received transfers.

@@

# Conclusion

@@

# References
